### 2017-01-28 thesis/results/results.tex
tmp commit

It was surprising that Creighton's metagene did not show significant association with \gls{bmi} in other data sets.

>>>>

Since Creighton's obesity associated genetic signature was not associated with sample \gls{bmi} or \gls{bmi} status in other data sets, Fuentes-Mattei's (FM) obesity associated genetic signature was examined to see whether FM's obesity metagene associated with sample \gls{bmi} or \gls{bmi} status.
Since FM's data set did not have sample \gls{bmi} information, FM's obesity metagene was not able to be compared with the sample \gls{bmi} or \gls{bmi} status in the original FM's data.
However, the transformation matrix was still applied to other cancer data to see whether FM's obesity metagene associated with sample \gls{bmi}/\gls{bmi} status

Firstly, FM's data was normalised with the \gls{rma} method and \gls{svd} was applied to the normalised data to get the transformation matrix.
The transformation matrix was used to transform the \gls{rma}-normalised Creighton's data to extract FM's obesity metagene scores.
FM's obesity metagene scores were compared with gene expressions and sample \gls{bmi}/\gls{bmi} status in Creighton's data, as shown in \cref{fig:fmmetacr1,fig:fmmetaboxcr1}.
Clearly, like with Creighton's obesity metagene, FM's obesity metagene was reflective of the overall gene expression of the samples, but did not associate with the sample \gls{bmi} or \gls{bmi} status.

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\hfill
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\caption[FM metagene and Creighton's cancer data]{(insert Creighton heatmaps)}
	\label{fig:fmmetacr1}
\end{figure}

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\hfill
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\caption[FM metagene and sample \gls{bmi}/\gls{bmi} status in Creighton's data]{(insert figure of box plot and scatter plot for Creighton data)}
	\label{fig:fmmetaboxcr1}
\end{figure}

Next, the transformation matrix was applied to the \gls{icgc} cancer data and resulting metagenes were compared with the gene expression and sample \gls{bmi}/\gls{bmi} status.
As evident in \cref{fig:fmmetaicgc1}, FM's obesity metagene scores appeared to reflect the gene expression of FM's obesity associated genetic signature.
However, as with all the results in this section so far, FM's obesity metagene did not significantly associate with any of the \gls{icgc} cancer data (\cref{fig:fmmetaboxicgc1}).

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\hfill
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\caption[FM metagene and \gls{icgc} cancer data]{(insert ICGC heatmaps)}
	\label{fig:fmmetaicgc1}
\end{figure}

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\hfill
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\caption[FM metagene and sample \gls{bmi}/\gls{bmi} status in \gls{icgc} data]{(insert figure of box plot and scatter plot for Creighton data)}
	\label{fig:fmmetaboxicgc1}
\end{figure}

Lastly, the transformation matrix was applied to Print's data.

\\

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\hfill
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\caption[FM metagene and Print's cancer data]{(insert Print heatmaps)}
	\label{fig:fmmetacris1}
\end{figure}

\begin{figure}[htp!]
	\centering
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\hfill
	\includegraphics[width=0.45\linewidth]{results1/crmeta_original}
	\caption[FM metagene and sample \gls{bmi}/\gls{bmi} status in Print's data]{(insert figure of box plot and scatter plot for Print's data)}
	\label{fig:fmmetaboxcris1}
\end{figure}

\noindent
